Seasonality in governing dynamics at submesoscales in the Kuroshio Extension

### 2016-06-28 writeup/rocha_etal.tex
Small edits

\section{Summary and Conclusion}
Our main finding is that in tidally forced global simulations the
near-surface upper-ocean inertia-gravity waves undergo
a strong seasonal cycle that is out-of-phase with the seasonal cycle of
submesoscale turbulence. \cite{dasaro1978} showed that velocity of linear internal waves
in the mixed-layer strongly depends on the density jump at the mixed-layer
base, with largest mixed layer velocities when the jump is strongest.
In Summer, the shallow mixed layer overlays a strong seasonal pycnocline,
and thus the internal waves projection onto the mixed-layer may be stronger
according to \cite{dasaro1978}'s arguments. An
alternative explanation is that the shape of the baroclinic modes
change seasonally. In particular the baroclinic modes are
significantly more surface intensified in late Summer/early Fall
 (supplemental material).
If the internal wave source has weak seasonal dependence, then a strong
seasonal cycle in the near-surface expression of internal waves is expected.
Internal tide generation does not show a seasonal modulation \citep[e.g.,][]{alford2003},
and therefore it is plausible to expect a strong seasonality in the near-surface
expression of internal tides and
other small-scale internal waves generated through internal tide interactions.
Near-inertial wave generation peaks in Winter, but those waves project on large
horizontal scales \citep[e.g, ][]{qi_etal1995}.

>>>>

\section{Summary and Conclusion}
Our main finding is that in tidally forced global simulations the
near-surface upper-ocean inertia-gravity waves in the Kuroshio Extension undergo
a strong seasonal cycle that is out-of-phase with the seasonal cycle of
submesoscale turbulence. \cite{dasaro1978} showed that velocity of linear internal waves
in the mixed-layer strongly depends on the density jump at the mixed-layer
base, with largest mixed layer velocities when the jump is strongest.
In Summer, the shallow mixed layer overlays a strong seasonal pycnocline,
and thus the internal waves projection onto the mixed-layer may be stronger
according to \cite{dasaro1978}'s arguments. An
alternative explanation is that the shape of the baroclinic modes
change seasonally. In particular the baroclinic modes are
significantly more surface intensified in late Summer/early Fall
 (supplemental material).
If the internal wave source has weak seasonal dependence, then a strong
seasonal cycle in the near-surface expression of internal waves is expected.
Internal tide generation does not show a seasonal modulation \citep[e.g.,][]{alford2003},
and therefore it is plausible to expect a strong seasonality in the near-surface
expression of internal tides and
other small-scale internal waves generated through internal tide interactions.
Near-inertial wave generation peaks in Winter, but those waves project on large
horizontal scales \citep[e.g, ][]{qi_etal1995}.
